% !TeX encoding = UTF-8
% !TeX spellcheck = en_GB
\section{Systems dependencies}

The list below, is the technolgies we are using in our application, group into categories of technogy. 

\subsection*{Project Start - choose framework}

\begin{itemize}
    \item Microsoft AspNetCore v2: For basis web framework to handle, request, athentication, 
    \item Dotnet API framework: For handling RESTFull API's 
    \item Swagger: For dotnet API visualization
    \item Microsoft EntityFrameworkCore version 8.x: For general handling dependency injection to a database connection. 
    \item Postgress v.8: Choosen database servere for this project. 
    \item Docker / Docker-compose / docker-swarm: For containerized applications 
    \item gravatar: For provide user profile images. 
    \item Github / Github actions/ Github secrets: For storing and deploying source code
    \item DigitalOcean: Production server for our application 
\end{itemize}


\subsection*{Monitoring}

\begin{itemize}
    \item prometheus/prometheus-net/prometheus-net.AspNetCore: For provide metrics to Grafana. 
    \item Grafana: For Data Visualization of data from prometheus and direct data from Postgress database. 
\end{itemize}

\subsection*{Logging}

\begin{itemize}
    \item Serilog AspNetCore v.8: For logging.
    \item Fluentd: For collecting logs from different sources. 
\end{itemize}


\subsection*{Software quality - Testing}

\begin{itemize}
    \item Sonarqube: Static analyzer for code quality and securit issues
    \item CodeClimate: Another static analyzer also for code quality and securit issues
    \item Playwright: UI testing 
    \item Cypress: End-2-end testing
    \item Xunit: For Basic Unit testing
\end{itemize}

